Effects of Weather on Maize Yield in Kenya

### 2019-01-17 presentations/January2019/presentation1.tex
presentation
work

\usepackage{amsmath}  
\usepackage{multirow,graphicx,array}
\usepackage{multicol}
\usepackage{hhline}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{threeparttable,booktabs}
\usepackage{chngcntr}
\usepackage{dcolumn}
\usepackage{caption}
\usepackage{fixltx2e}
\usepackage{rotating}
\usepackage{amssymb}
 \usepackage{setspace}

\usetheme{Singapore}
\useoutertheme{miniframes}
\AtBeginSection[]{\subsection{}}

@@

\title{Effects of Weather on Maize Yield in Kenya}  
\author{Monika Novackova \\ \footnotesize supervised by: \textcolor{darkblue}{Pedram Rowhani, Martin Todd and Annemie Maertens}}

@@

@@

\vspace{0.3cm}
\vspace{0.3cm}a
\\
\vspace{0.3cm}a
\\
\vspace{0.3cm}a
}

\frametitle{Effects of droughts on economy}\label{Effects} 
\begin{block}{\textbf{Computable General Equilibrium (CGE)} Models }
\begin{itemize}

\item \underline{\textbf{\cite{OxfamIDS}}}
\begin{itemize}
\item Exploring range of scenarios for food price increase in 2030
\begin{itemize}
\item 1. Baseline 2. Climate change 3. Climate change with adaptation 4. Adaptation only in sub-Saharan Africa
\end{itemize}
\item Global coverage, set of individual country models, linked through international trade
\item Climate change (incl. drought) modelled as changes in factor productivity (usually negative)

\end{itemize}
\end{block}
\end{frame}

\section{My Suggestion}

\frametitle{My suggestion - panel estimation}\label{MySuggestion1}

My interest: \textbf{Effects of drought on economy in Kenya}
\begin{itemize}

\item \textbf{Response variable}

\begin{itemize}
\item Volumes of production (crop specific, total)
\item Profit per acre \normalsize{\citep{Deschenes2007Ric}}

\begin{itemize}
\item \footnotesize{(Value of agricultural products - prod. expanses)/acres (crops, pasture, grazing)}\\ 
\end{itemize}
\end{itemize}
\item \textbf{Units of analysis}
\begin{itemize}
\item Counties in Kenya $\times$ year
\
\end{itemize}

\item \textbf{Explanatory variable of interest}

\begin{itemize}
\item Dummy variable (0/1) drought occurred in a particular county and year or not
\item Several varieties - various specifications of drought:

\note{also I can try some t-tests, f-test for various grouping - WHAT WOULD BE THE BEST DEFFINITION OF DROUGHT year x county\\
\vspace{0.3cm}a\\
\vspace{0.3cm}}

\frametitle{My idea - panel estimation}\label{MySuggestion4}

\begin{align*}
\begin{array}{lcl}
 Y_{i,t} &=& \alpha_i +\gamma_t + \delta D'_{i,t} +  \boldsymbol{\beta X_{i,t}}+ \epsilon_{i,t}
\end{array}
\end{align*}

\begin{table}
\begin{small}
\begin{tabular}{lll}

$Y_{i,t}$ &$=$& Response variable (food production/price), county $i$ in year $t$\\
$\alpha_i$ &$=$& Fixed effects, county $i$\\
{\color{darkblue}$\delta$ }&{\color{darkblue}$=$}&{\color{darkblue}{Effect of drought on economy}}\\
$D_{i,t}$ &$=$& Indicator variable\\
& &  $D=1$ if drought in county $i$ in year $t$, $D=0$ otherwise\\
$\boldsymbol{\beta}$ &$=$& Vector of effects of other covariates\\
$X_{i,t}$ &$=$& Matrix of values of other covariates in county $i$ in year $t$\\
$\epsilon_{i,t}$ &$=$& Error term \\
{\color{DarkGreen}$\gamma_t$} & {\color{DarkGreen}$=$}& {\color{DarkGreen}Year specific indicator?}
\end{tabular}
\end{small}
\end{table}

\note{Also waldtest, jako ekvivalent pro celkovy f-test byl signifikantni>> overall fit je moc o}

>>>>

\usepackage{amsmath}  
\usepackage{multirow,graphicx,array}
\usepackage{multicol}
\usepackage{hhline}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{threeparttable,booktabs}
\usepackage{chngcntr}
\usepackage{dcolumn}
\usepackage{caption}
\usepackage{fixltx2e}
\usepackage{rotating}
\usepackage{amssymb}
 \usepackage{setspace}
\usepackage{changepage}
\usetheme{Singapore}
\useoutertheme{miniframes}
\AtBeginSection[]{\subsection{}}

@@

\title{Effects of Weather on Maize Yield in Kenya}  
\author{Monika Novackova \\[2mm] \footnotesize supervised by: \textcolor{darkblue}{Pedram Rowhani, Martin Todd and Annemie Maertens}}

@@

\frametitle{Model specification}\label{spec}

Error structure, ARMA, AIC

\note{

\vspace{0.3cm}
\vspace{0.3cm}a

}

\section{Results}

\frametitle{Results}\label{Results} 
{\begin{threeparttable}
\caption{\normalsize{\textbf{ {Mixed  effects model:}} exponents of the coefficient estimates Log of maize yield and weather, ARMA(1,1) errors}}
%KEN11dK  KEN11dK_ASAL    KEN11dK_nonASAL										
\label{KenARe11_exponents} 
\setstretch{1.33}
\begin{tabular}{@{}lllllll} 
 \\
  \textbf{Fixed effects:}&\textit{\textbf{All counties}}&\textit{\textbf{ASAL}}&\textit{\textbf{non-ASAL}}\\
\vspace{-0.2cm}Intercept&$1.296^{***}$&$1.272^{*}$&$1.408^{**}$\\
 \vspace{-0.2cm}Prec. total&$1.081^{*}$&$1.007^{}$&$1.277^{***}$\\
  \vspace{-0.2cm}Prec. total sq.&$0.973^{*}$&$1.003$&$0.881^{***}$\\
 \vspace{-0.2cm}Prec. c. of var.&$0.924^{\bullet}$&$0.970$ &$0.907^{}$\\
 \vspace{-0.2cm}Dry spell -length\tnote{a}&$0.935^{*}$&$0.834^{**}$&$ 0.988^{}$\\
 \vspace{-0.2cm}Dry spells $\geq~4$ d.\tnote{b}&$0.939^{*}$&$0.855^{**}$&$0.989^{}$\\
 \vspace{-0.2cm}Temp. - average&$0.820^{***}$&$0.808^{*}$&$0.880$ $^{}$\\
 \vspace{-0.2cm}Temp. c. of var.&$1.043^{\bullet}$&$1.032$&$1.060$ ${*}$\\
  \hline
\textit{Number of observations:}  &\multicolumn{2}{l}{$1300$}&\multicolumn{2}{l}{$698$}&\multicolumn{2}{l}{$602$}
\\
\end{tabular} 
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} Standard errors in brackets; \hfill $^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
            \begin{adjustwidth}{1cm}{} 
  \item[a] Length of the longest dry spell in number of days.
    \item[b] Number of dry spells lasting for four days or longer. 
     \end{adjustwidth}
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable}\par }
\end{frame}

\note{

\vspace{0.3cm}
\vspace{0.3cm}a

}

@@

\vspace{0.3cm}
\vspace{0.3cm}a

}
